14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-18 rules/rules19.tex
Rules: Add comments.

\header{System description.}
%
\todo{add minimum requirement for authorship?}
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}

\header{Multiple versions.}
%
The organizers' intent is to promote as wide a comparison among
solvers and solver options as possible.  However, if the number of
solver submissions is too large for the computational resources
available to the competition, the organizers reserve the right not to
accept multiple versions of solvers from the same solver team.

@@

\header{Input and output.}
%
In the \maintrack and \ucoretrack, a participating solver must read a
single benchmark script, whose filename is presented as the solver's
first command-line argument.  In the incremental track, a trace
executor will send commands from a benchmark script to the solver's
standard input channel.

>>>>

\header{System description.}
%
\todo{add minimum requirement for authorship?}
As part of the submission, SMT-COMP entrants are \emph{required} to provide a
short (1–-2 pages) description of the system.  This should include a list of
all authors of the system, their present institutional affiliations, and any
appropriate acknowledgements.  The programming language(s) and basic SMT
solving approach employed should be described (e.g., lazy integration of a
Nelson-Oppen combination with SAT, translation to SAT, etc.).  System
descriptions should also include a URL for a web site for the submitted tool.
System descriptions must be submitted until the final solver deadline System
descriptions will be made publicly available. \todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
\an{This todo should actually go into section 5, intro of the section maybe, we should add there that solvers will be archived on the website and so on. Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}

\header{Multiple versions.}
%
The intent of the organizers is to promote as wide a comparison among
solvers and solver options as possible.  However, if the number of
solver submissions is too large for the computational resources
available to the competition, the organizers reserve the right not to
accept multiple versions of solvers from the same solver team.

@@

\header{Input and output.}
%
In the \maintrack, \mvaltrack, \ucoretrack and \challtrack, a participating
solver must read a single benchmark script, whose filename is presented as the
solver's first command-line argument.  In the \inctrack, a trace
executor will send commands from a benchmark script to the solver's standard
input channel.
